Supplemental Materials for: Meta-analytic approaches and new effect sizes to account for heterogeneous effects in comparative physiology

### 2021-07-12 MS/supp.Rmd
Updating download file from OSF because API is a pain in the butt. Fixed now, so just need to link to file and should download

# Citation
This supplement is asscoaited with a special issue review paper and can be cited as follows:

@@

```{r loadpackages, echo = TRUE, class.source='klippy'}
pacman::p_load(png, jpeg, pander, cowplot, flextable, tidyverse, metafor, orchaRd, here)

@@

# Example on how to download and load for reader. Should work anyway. Needs some testing
download.file(url="https://ndownloader.figshare.com/files/7714777", destfile = "CaseStudy1.csv")

data_CS1 <- read.csv(here("CaseStudy1.csv"))

@@

# Case Study 2:
```{r class.source='klippy'}
download.file(url="REPLACE URL FROM OSF HERE", destfile = "CaseStudy2.csv")

data_CS1 <- read.csv(here("CaseStudy2.csv"))

>>>>

# Citation
This supplement is associated with a special issue review paper and can be cited as follows:

@@

```{r loadpackages, echo = TRUE, class.source='klippy'}
pacman::p_load(png, jpeg, pander, cowplot, flextable, tidyverse, metafor, orchaRd, here, osfr)

@@

# Example on how to download and load for reader. Should work anyway. Needs some testing
osfr::osf_retrieve_file("https://osf.io/mnw5d/") %>% osfr::osf_download()

data_CS1 <- read.csv(here::here("CaseStudy1.csv"))

@@

# Case Study 2:
```{r class.source='klippy'}

osfr::osf_retrieve_file("https://osf.io/mnw5d/") %>% osfr::osf_download()

data_CS1 <- read.csv(here::here("BPA_example.csv"))

```{r}
